
Similarly, under a strategy account it is not the intent to encode per se, but rather the type of processing intent to encode fosters that generates contiguity. Deliberately form associations by . We can ask them to form such a chain by telling a story... 


The critical difference between a encoding strategy account and context drift account is the type of processing being carried out. Neither theory really claims that intent per se is key in generating a contiguity effect. Instead they suggesst that intent engenders a particular type of processing that fosters contiguiyu. The two accounts differ fundmentally, however, on what that type of processing is. 



By contrast, the encoding strategy account suggest it has nothing to do with the drift of mental context, it is a delebrate attempt to process the relationships among items, not necessairly an attempt to encode, but to process in a wat as to to think back to previous items even after those items have disappeared. That is, participants are deliberately trying to make connections between the items. This critical aspect of the strategy account does not inherently depend on an itent to encode and can be captured by setting up an implicit encoding task that requires a similar sort of processing. 






Indeed strong version of the context account says that any residue of the past is due to autocorrelations in the drift of tmporal contetx that do not depend on any dilivberate attempt to preserve the past. That is, although there is no doubt that subject do indeed engage in dilebrate attempts to think back to previous items and form associations among them, such relational processing is not necessary for temporal contiguirty. This can be captured by an implicit encoding condition that does not require relational processing, but \emph{is} likley to promote context dfirt.

Therefore, the contrast between the forming an image of a single item on the one hand and forming an image that incoporates previous items on the other hand, captures the kernel of the distinction between the context and encoding strategy accounts.